Extended Abstract: Grounding Language to Reward Functions With Abstract Markov Decision Processes

### 2016-05-05 paper/paper-template-latex/paper_template.tex
Add updated paper

\section{Introduction}
The issue of abstraction is key to the field of reinforcement learning as it represents a logical way to accelerate planning time within sequential decision making problems by breaking apart large, complex tasks into smaller sub-tasks. Most often, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism for reinforcement learning. Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or simply pruning irrelevant states from consideration. Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``action''. Unfortunately, many of these methods fall short in that they simply add more elements to either the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.

Our approach in tackling this problem of abstraction is to utilize abstract Markov decision processes (AMDPs) which represent a decomposition of a regular MDPs creating multiple layers of abstraction. To briefly summarize, MDPs are represented by the five-tuple: $\langle$ ${\cal S}$, ${\cal A}$, ${\cal T}$, ${\cal R}$, $\gamma$ $\rangle$, where ${\cal S}$ is a set of states of the world; ${\cal A}$ is a set of actions that the agent can take; ${\cal T}$ is a function that computes the probability of transitioning from one state to another via applying a specified action; ${\cal R}$ is a function specifying the agent's reward for taking an action within a particular state ; and $\gamma$ is a discount factor. AMDPs take on a slightly different form by maintaining a stack of internal MDPs, each of which represents a different layer of abstraction for the input problem. The base level MDP represents the original task as it was given, while higher level MDPs are hard coded over abstracted state and action spaces (with corresponding transition dynamics and reward functions). These higher level MDPs capture the notion of sub-goals within the problem and so whenever the agent in a lower level need take an action, the current state information is fed upward to the next highest level of the AMDP. Once the highest MDP is reached, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level which is then stored and reused so as to avoid redundant computation. Surjective state mappings are maintained from higher to lower level MDPs allowing for a backpropagation to occur once a higher level sub-task has been solved and this process then repeats onnce the backpropagation returns all the way down to the base level MDP. It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs.

In order to examine the effectiveness of the abstraction imposed by AMDPs, we extend prior work by MacGlashan et.al. on grounding natural language commands to the reward function of an MDP~\cite{MacGlashan2015GroundingEC}. In particular, we take an AMDP and evaluate the effectiveness of grounding a reward function at each level of the AMDP using natural language commands taken individually from each level of abstraction. In the context of the cleanup world domain used by MacGlashan et.al., this corresponds to an AMDP with three layers of abstraction: high, mid, and low.

We take a natural language command from an arbitrary level and apply IBM Model II translation to ground it to a reward function for each level of the AMDP.

We show that grounding an arbitrary natural language command to a reward function will be most successful when the natural language command and MDP correspond to the same level of abstraction. For the purpose of staying consistent with the experimental method used by MacGlashan et.al., we will leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within BURLAP to conduct experiments and collect results.

\section{Section}

Section text here.

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{RSS citations}

Please make sure to include \verb!natbib.sty! and to use the
\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
citation commands, most usefully \verb!\citet!. For example, rather than the
awkward construction

{\small
\begin{verbatim}
\cite{kalman1960new} demonstrated...
\end{verbatim}
}

\noindent
rendered as ``\cite{kalman1960new} demonstrated...,''
or the
inconvenient

{\small
\begin{verbatim}
Kalman \cite{kalman1960new}
demonstrated...
\end{verbatim}
}

\noindent
rendered as
``Kalman \cite{kalman1960new} demonstrated...'',
one can
write

{\small
\begin{verbatim}
\citet{kalman1960new} demonstrated...
\end{verbatim}
}
\noindent
which renders as ``\citet{kalman1960new} demonstrated...'' and is
both easy to write and much easier to read.

\subsection{RSS Hyperlinks}

This year, we would like to use the ability of PDF viewers to interpret
hyperlinks, specifically to allow each reference in the bibliography to be a
link to an online version of the reference.
As an example, if you were to cite ``Passive Dynamic Walking''
\cite{McGeer01041990}, the entry in the bibtex would read:

{\small
\begin{verbatim}
@article{McGeer01041990,
  author = {McGeer, Tad},
  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}},
  volume = {9},
  number = {2},
  pages = {62-82},
  year = {1990},
  doi = {10.1177/027836499000900206},
  URL = {http://ijr.sagepub.com/content/9/2/62.abstract},
  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html},
  journal = {The International Journal of Robotics Research}
}
\end{verbatim}
}
\noindent
and the entry in the compiled PDF would look like:

\def\tmplabel#1{[#1]}

\begin{enumerate}
\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
1990.
\end{enumerate}
%
where the title of the article is a link that takes you to the article on IJRR's website.

Linking cited articles will not always be possible, especially for
older articles. There are also often several versions of papers
online: authors are free to decide what to use as the link destination
yet we strongly encourage to link to archival or publisher sites
(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
the extent possible.

@@

The conclusion goes here.

>>>>

\section{Introduction}
When dealing with the issue of efficiently solving large-scale sequential decision making problems defined by complex state-action spaces, the ability to identify and leverage multiple layers of abstraction is key. Developing good methods of abstraction represents a logical way to accelerate planning time by breaking apart large, complex tasks into smaller sub-tasks. Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and achieving sub-goals. Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilize multiple layers of abstraction over all components of the Markov Decision Process (MPD) in order to efficiently learn in complex domains. In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the abstraction based on the success of these groundings.

\section{Prior Work}
Typically, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism in the hopes of improving overall problem tractability. Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or intelligently pruning states that are irrelevant to the overall task from consideration. Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``action''. Unfortunately, these methods suffer from potentially increasing the size of the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.

\section{Abstract Markov Decision Processes}

Our approach in tackling this problem of abstraction is to utilize abstract Markov decision processes (AMDPs) which represent a decomposition of a regular MDP resulting in a tiered hierarchy where each level represents an abstraction over the previous one. To briefly summarize, MDPs are represented by a five-tuple: $\langle$ ${\cal S}$, ${\cal A}$, ${\cal T}$, ${\cal R}$, $\gamma$ $\rangle$, where ${\cal S}$ is the set of possible states in the world; ${\cal A}$ is a set of all available actions that can be executed; ${\cal T}$ is a function that computes the probability of transitioning from one state to another by executing an action; ${\cal R}$ is a function specifying the agent's reward for taking an action within a particular state ; and $\gamma$ is a discount factor.

Building on top of this, AMDPs take a layered approach by maintaining a stack of MDPs, each of which represents a different layer of abstraction for the input problem. The base (lowest) level MDP is always the MDP representing the original problem while higher level MDPs are hard coded over smaller state and action spaces (with corresponding transition dynamics and reward functions). Each state and action in a higher level MDP is implemented as an abstraction over multiple states and actions in the lower level creating a many-to-one mapping (as we move up the stack) resulting in smaller, more tractable state-action spaces. Intuitively, moving up the stack of MDPs captures the notion of identifying smaller, easier sub-goals within the problem. In terms of execution, a learning agent always begins at the base level MDP; whenever an action must be selected at a lower level, the current state information is fed upward and mapped to the next highest level of the AMDP effectively forcing the agent to think at one higher level of abstraction. This process repeats until the top of the MDP stack is reached, at which point, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level (which is then stored and reused so as to avoid redundant computation). Given this policy, the action required at highest level of abstraction becomes known and a series of surjective state mappings are maintained from higher to lower level MDPs allowing for a sort of backpropagation to occur once a higher level sub-task has been solved. This process of mapping backwards, computing a policy, and taking the specified action then repeats all the way down back to the base level MDP. It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs each of which is decreasing in size and complexity as we move up the AMDP stack.

\section{Evaluation}

\subsection{Experiments}

In order to examine the effectiveness of the abstractions imposed by these Abstract Markov Decision Processes (AMDPs), we extend prior work by MacGlashan et. al. on grounding natural language commands to the reward function of a Markov Decision Process (MDP). The primary contribution of this prior work is the ability to represent tasks as MDP reward functions and further combine learning from demonstration methods with language models to directly embed a user's verbal command into the reward function~\cite{MacGlashan2015GroundingEC}. Specifically, given a dataset of natural language commands and their associated task demonstrations, inverse reinforcement learning (IRL) is applied to the demonstrations in order to inform a distribution over possible reward functions which is then used to train a language model in a weakly supervised fashion. The authors followed the paradigm set up in MacGlashan et. al. and used an IBM Model II Translation System for translating between natural language and reward functions (machine language), augmented by the provided demonstration. More specifically, we modify the IBM Model II decoding procedure to weight the probability of a given translation (the probability of a machine language command given the source language command) by the probability of the machine language command given the provided demonstration. With this process, the success of the resultant models in grounding reward function tasks is dependent on both the various natural language commands across the dataset as well as the provided demonstrations.

We show that grounding an arbitrary natural language command to a reward function will be most successful when the natural language command and reward function correspond to the same level of abstraction. Staying consistent with the experimental method used by MacGlashan et.al., we leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within the Brown-UMBC Reinforcement Learning and Planning library (BURLAP) to conduct our experiments. As with MacGlashan et. al. we use the Cleanup World Domain inspired by Sokoban \cite{Junghanns2001SokobanEG}.
% INSERT FIGURE

We build our own AMDP over this domain, with each level corresponding to a different level of abstraction. There are three levels: \textbf{low}, \textbf{mid}, and \textbf{high}. The low-level MDP corresponds to simple directional commands, like telling the agent to move north, south, east, and west. The mid-level MDP corresponds to commands referencing the agent, the block, the doors in each of the domain's three rooms, and the rooms themselves. Finally, the high-level MDP abstracts away doors, so that these commands only reference agents, blocks, and rooms.

To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands and their respective demonstrations. The following are some examples of natural language commands at each level of the AMDP:

\begin{description}
\item[\textbf{Low:}] Go three steps south, then two steps east.
\item[\textbf{Mid:}] Go to the red door, then go into the red room.
\item[\textbf{High:}] Go to the green room.
\end{description}

Our experiment consists of training IBM II Translation Models between every permutation of the levels of the AMDP. More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP. We then
\subsection{Results}

Lorem ipsum

@@

Lorem ipsum
